### 2014-10-28 fundamentals/impl.tex
tables where I put them
reduces the chaos in the bibliographies to just one file of chaos
note about robert's htc usage

Cyclopts (\TODO{cite}), a proof of principle design and implementation of such a
system, uses UW-Madison's HTCondor HTC infrastructure to perform sensitivity
studies on \Cyclus' resource exchange optimization solvers. To date, it has been
used run over $10^4$ jobs, or (\TODO{compute time}) total compute hours, using
the \Cyclus library via its resource exchange \gls{API}.

@@

\begin{figure}[htbp!]
\begin{center}
\includegraphics{./images/modifiedopen.eps}
\end{center}
\caption{The \Cyclus framework enables fully open, partially open, and fully
closed collaborations\cite{wilson_cyclus:_2012}.}
\label{fig:modifiedopen}
\end{figure}

@@

\begin{table}
\centering
\begin{tabularx}{\textwidth}{|r|l|l|}
\hline
\textbf{Agent Type} & \textbf{Archetype} & \textbf{Functionality} \\
\hline
Facility & BatchReactor & A reactor model that handles batch refuelling, based on pre-determined recipes of compositions. \\
Facility & Source & This facility generates material of the composition and commodity type specified as input.  \\
Facility & Sink & This facility is capable of accepting a finite or infinite quantity of some commodity produced in the simulation \\
Facility & EnrichmentFacility & This facility enriches uranium at a specified capacity. \\
Institution& ManagerInst & The manager institution manages production of commodiites among its facilities by building new necessary ones \\
Institution & DeployInst &  This institution deploys specific facilities as defined explicitly in the input file. \\
Region & GrowthRegion & This region determines whether there is a need to meet a certain capacity (as defined via input) at each time step \\
\hline
\end{tabularx}
\caption{The Archetypes in \Cycamore seek to cover a large range of simple simulation use cases.}
\label{tab:cycamore}
\end{table}

>>>>

Cyclopts (\TODO{cite}), a proof of principle design and implementation of such a
system, uses UW-Madison's HTCondor HTC infrastructure to perform sensitivity
studies on \Cyclus' resource exchange optimization solvers. To date, it has been
used run over $10^4$ jobs, or (\TODO{compute time}) total compute hours, using
the \Cyclus library via its resource exchange \gls{API}.
The HTC infrastructure has also been utilized to run and collect
information from full \Cyclus simulations running in parallel on $10^3$
machines reliably for order $10^5$ simulations.

@@

\begin{figure}[htbp!]
\begin{center}
\includegraphics{./images/modifiedopen.eps}
\end{center}
\caption{The \Cyclus framework enables fully open, partially open, and fully
closed collaborations\cite{carlsen_cyclus_2014}.}
\label{fig:modifiedopen}
\end{figure}

@@

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{|r|l|X|}
\hline
\textbf{Agent Type} & \textbf{Archetype} & \textbf{Functionality} \\
\hline
Facility & BatchReactor & A reactor model that handles batch refuelling, based on pre-determined recipes of compositions. \\
Facility & Source & This facility generates material of the composition and commodity type specified as input.  \\
Facility & Sink & This facility is capable of accepting a finite or infinite quantity of some commodity produced in the simulation \\
Facility & EnrichmentFacility & This facility enriches uranium at a specified capacity. \\
Institution& ManagerInst & The manager institution manages production of commodiites among its facilities by building new necessary ones \\
Institution & DeployInst &  This institution deploys specific facilities as defined explicitly in the input file. \\
Region & GrowthRegion & This region determines whether there is a need to meet a certain capacity (as defined via input) at each time step \\
\hline
\end{tabularx}
\caption{The Archetypes in \Cycamore seek to cover a large range of simple simulation use cases.}
\label{tab:cycamore}
\end{table}
